---
title: "Hw5"
author: "Jingwei Ren"
date: "11/7/2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(ggplot2)
```

###problem 1

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r,csv_file}
data = 
  tibble(file_name = list.files(path = './data')) %>% 
  mutate(name = map(.x = str_c("./data/", file_name),~read.csv(.x))) 

data = data %>%
  unnest() %>% 
  separate(file_name, into = c("arm", "id"), sep = "_",remove = F) %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  separate(week, into = c("rm", "week"), sep = "_") %>%
  separate(id, into = c("id", "csv"), sep = ".csv") %>%
  select(-csv, -rm)
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r, spaghetti}

data %>% 
   mutate(week = as.numeric(week))%>%
  ggplot(aes(x = week, y = observation,color = id))+
  geom_line() +
  facet_grid(~arm)+
  labs(
    title = "Observations on Each Subject over Time",
    x = "Week",
    y = "Observation",
    caption = "Data from a longitudinal study") +
  theme(legend.position = "bottom")
```


